### 2019-05-10 main.tex
Add longtable

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.8]{FiraMono}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2.1cm, bottom=2.1cm, left=2.1cm, right=2.1cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage{hyperref}

@@

More recently, scholars have argued that polycentric governance approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}. Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}. Experiences such as inshore fisheries in Turkey or timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}. Authors also point out that polycentrism promotes quick adaptation to bad use of public resources because of continuous experimentation at smaller scales \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.

% Rewrite last sentence

@@

% Maybe write a paragraph about elites and veto players?

@@

We chose to survey Latin American elites for several reasons. First, Latin America is the most bio-diverse region in the world. The Amazon river basin is the largest preserved forest on Earth, and it contains about half of the world's carbon stock \citep{yang2018post}. Second, the region remains largely dependent on agriculture, so global warming will severely disrupt Latin American economies \citep{jones2003potential}. Lastly, Latin American elites have vast disagreements about societal issues. For instance, the rapid shifts between leftist and rightist governments, along with growing ideological polarisation in the region, indicate that local elites are not a cohesive social group  \citep{ellner2019pinktide}. Latin American elites are capable of influencing if climate change solutions are pursued, but they might disagree more on which particular solutions to pursue.

We formulate our experiment according to Elinor Ostrom's `design principles' of successful common pool resource management and selected our category values according to them \citep{ostrom1990governing, bechtel2013mass}. The hypothetical climate change agreements includes six dimensions: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. Table~\ref{tab:categories} describes the values we included in each design principle. \\

\begin{table}[ht]
  \begin{center}
      \caption{\textbf{Design principles for climate change mitigation conjoint experiments.}}
      \label{tab:categories}
    \begin{tabular}{l|l}
      \toprule
      \textbf{Design principle} & \textbf{Values} \\
      \midrule
      Who makes the rules? & International organisations \\ 
	  & Federal government \\ 
	  & Local government \\ 
	  & Local community members \\
	  & Non-Governmental organisations \\
	  & \\
      Conflict resolution mechanism & United Nations \\
	  & Government bureaucracy \\
	  & Local courts \\
	  & Private arbitration \\
	  & Informal norms \\
	  & \\
      Punishment & Imprisonment \\
	  & Fines \\
	  & Blacklist \\
	  & None \\
	  & \\
	  Punishment for repeated violations & More penalty \\
	  & Same \\
	  & Less penalty \\
	  & \\
	  Agreement costs & Rich countries pay more than poor countries \\
      & Proportional to history of emissions \\ 
      & Proportional to current emissions \\
	  & Only rich countries pay\\
	  & \\
	  Renegotiation & Never \\
	  & Fifty years \\
	  & Twenty years \\
	  & Five years \\
	  & One year \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{titling}
\usepackage{lscape}
\usepackage{amssymb, amsmath, amssymb}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{longtable}
\usepackage[stable]{footmisc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=.8]{FiraMono}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{dcolumn}
\usepackage{mathtools}
\usepackage{caption}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage[authoryear]{natbib}
\usepackage{babelbib}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=10000
\clubpenalty=10000
\setcitestyle{aysep={}} 
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
\makeatother
\usepackage{hyperref}

@@

More recently, scholars have argued that polycentric approaches provide a better `institutional fit' for natural resource systems \citep{turnheim2018innovating,berkhout2003negotiating, carlisle2017polycentric, ostrom1990governing}. Polycentrism is defined as a political arrangement in which formally independent units operating at different levels engage in a continuous process of cooperation and competition \citep{cole2015advantages,aligica2013co}. Experiences such as inshore fisheries in Turkey and timber management in Switzerland show that polycentrism induces individual cooperation and allows communities to avoid the `tragedy of the commons', that is, the overexploitation of shared resources \citep{hardin1968tragedy, ostrom1990governing}. Authors also point out that polycentric systems improve accountability as decentralisation reduces rent-seeking opportunities for interest groups \citep{turnheim2018innovating,ostrom2012nested,ostrom2014polycentric,sovacool2013adaptation}.

@@

Self-enforcing environmental governance faces further difficulties in new democracies. In Latin America, authoritarian regimes discouraged civil participation and reduced social capital, two requirements for effective polycentric arrangements \citep{aligica2014institutional,ostrom1990governing}. Top-down climate policies also create incentives for organised groups to collude with state officials and pursue private interests. In that scenario, elites and state representatives have \textit{de facto} veto power over environmental legislation and can override local decisions to their own benefit.

@@

We conducted our experiment in 10 Latin American countries. Latin America is the most biodiverse region in the world and it remains largely dependent on agriculture, thus global warming can severely disrupt the regional environment and economy \citep{jones2003potential, yang2018post}. Moreover, survey experiments on climate policies have focused on a small set of developed countries, so truly comparative experimental work is still scarce. We fill this gap by including countries in South, Central, and North America where local elites have different stakes at climate change negotiations.

The hypothetical climate change agreements includes six dimensions: 1) which organisation defines the rules; 2) how would conflicts be resolved; 3) what punishment should be applied to rule-breakers; 4) how should repeated violations be sanctioned; 5) which countries should bear the costs of the agreement; 6) how often should the agreement be renegotiated. The categories map conceptual differences between polycentric and state-led climate mitigation policies \citep{bechtel2013mass, ostrom1990governing}. Table~\ref{tab:categories} describes the values we included in each design principle. \\

\begin{longtable}{l|l}
\caption{Design principles for climate change mitigation conjoint experiments} \label{tab:categories} \\

\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}}\\ \hline 
\endfirsthead

\multicolumn{2}{c}%
{{\tablename \thetable{} Design principles for climate change mitigation conjoint experiments (\textit{cont.})}} \\
\hline \multicolumn{1}{c|}{\textbf{Attribute}} & \multicolumn{1}{c}{\textbf{Values}} \\ \hline 
\endhead

\hline \multicolumn{2}{r}{{\textit{Continued on next page}}} 
\endfoot

\hline
\endlastfoot

Who makes the rules? & International organisations \\ 
& Federal government \\ 
& Local government \\ 
& Local community members \\
& Non-Governmental organisations \\
& \\
Conflict resolution mechanism & United Nations \\
& Government bureaucracy \\
& Local courts \\
& Private arbitration \\
& Informal norms \\
& \\
Punishment & Imprisonment \\
& Fines \\
& Blacklist \\
& None \\
Punishment for repeated violations & More penalty \\
& Same \\
& Less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries \\
& Proportional to history of emissions \\ 
& Proportional to current emissions \\
& Only rich countries pay\\
& \\
Renegotiation & Never \\
& Fifty years \\
& Twenty years \\
& Five years \\
& One year\\
\end{longtable}
